### 2014-11-13 tex/related.tex

\subsection{Symbolic Exection}
As originally formulated, symbolic execution was incapable of reasoning beyond scalar input values. Since then, several adaptations to allow symbolic execution to cope with heap data structures have been proposed, beginning with Generalized symbolic execution \cite{GSE03}. Subsequent improvements to the method \cite{Deng:2006,Deng:2007} reduce path explosion by delaying path splitting over aliasing choices for as long as possible. However, since all of the above methods introduce nondeterminism during field reads and writes, they all contribute to path explosion to some extent. Since our heap representation does not introduce any nondeterminism beyond the level in standard symbolic execution, it will generally create fewer paths than these methods, sometimes by a wide margin.

\subsection{Model Checking}
Need to talk about Bounded Model Checking, etc.

\subsection{Static Analysis}
A number of static analysis techniques have been proposed that have some ability to reason about input heap structures. These techniques are usually over-approximations, often have difficulty reasoning about path-sensitive properties, or cannot reason about programs with recursive data structures. Moreover, static analysis methods are seldom useful for test-case generation.

One notable static analysis method that is closely related to ours is the procedure summaries proposed by Isil and Tomas Dillig \cite{Dillig:2011}. Elements of their technique that are similar to ours include; references guarded by constraint expressions, conditional write semantics, and a general aversion to path splitting. However, their method is limited by most of the standard problems with static analysis techniques, including path sensitivity, imprecision, and recursive data structures. While their method has improved path sensitivity over standard static analysis methods, it remains limited by a statically-generated symbolic input heap, and cannot adapt to path-sensitive heap properties of the input heap. Thus, their method cannot determine a priori which nodes in the input heap are actually accessed by the program. It may potentially generate input heaps containing a significant number of nodes that have no impact on program execution.

\subsection{Heap Representations}
One significant line of work on representing heaps is shape analysis. Shape analysis attempts to reduce the complexity of the heap by combining multiple nodes with similar properties into summary nodes. The summary nodes typically establish may/must constraints over the heap structure, and typically represent an overapproximation of the represented heap. As such, program evaluations using shape analysis representations are prone to reporting large numbers of false positives.

>>>>

%\subsection{Symbolic Exection}

Recent years have seen a significant growth in research projects based
on symbolic execution, first introduced in the 1970's by
Clarke~\cite{Clarke:76} and King~\cite{King:76}.  These projects have
pursued three primary research directions to enhance traditional
symbolic execution: (1)~to improve its
effectiveness~\cite{Godefroid:PLDI05,Sen:FSE05,CadarEngler05EXE,KiasanKunit,Pasareanu:2011};
(2)~to improve its
efficiency~\cite{AnandETAL2009AbsSymExe,KhurshidSuen2005AbsSymExe,Godefroid:POPL07,Inkumsah:2008,ChangPhD10DataFlowSymbolicExecution,Santelices:ISSTA10,Visser:2012};
and (3)~to improve its
applicability~\cite{Person:FSE08,KhurshidETAL05RepairingStructurally,CsallnerETAL08DySy,SeoETAL06EnergyConsumptionFrameworkDistributedJava,Geldenhuys:2012,Ma:2011}. Handling
unbounded data input of complex type has continued to be a challenge
for symbolic execution.  Generalized symbolic execution \cite{GSE03}
with lazy initialization set the path to materializing fields
concretely. Subsequent improvements to the method
\cite{Deng:2006,Deng:2007} to reduce path explosion by delaying path
splitting over aliasing choices for as long as possible. However,
since all of the above methods introduce nondeterminism during field
reads and writes, they all contribute to path explosion to some
extent.

% Since our heap representation does not introduce any nondeterminism
%beyond the level in standard symbolic execution, it will generally
%create fewer paths than these methods, sometimes by a wide margin.

%\subsection{Model Checking} Need to talk about Bounded Model
%Checking, etc.

%\subsection{Static Analysis}

A number of static analysis techniques have been proposed that have
some ability to reason about input heap structures. One notable static
analysis method that is closely related to ours is the procedure
summaries proposed by Isil and Tomas Dillig \cite{Dillig:2011}.  While
their method has improved path sensitivity over standard static
analysis methods, it remains limited by a statically-generated
symbolic input heap, and cannot adapt to path-sensitive heap
properties of the input heap.

% These techniques are usually over-approximations, often have
% difficulty reasoning about path-sensitive properties, or cannot
% reason about programs with recursive data structures. Moreover,
% static analysis methods are seldom useful for test-case generation.

%. Elements of their technique that are similar to ours include;
%references guarded by constraint expressions, conditional write
%semantics, and a general aversion to path splitting. However, their
%method is limited by most of the standard problems with static
%analysis techniques, including path sensitivity, imprecision, and
%recursive data structures.

% Thus, their method cannot determine a priori which nodes in the
%input heap are actually accessed by the program. It may potentially
%generate input heaps containing a significant number of nodes that
%have no impact on program execution.

%\subsection{Heap Representations}

%One significant line of work on representing heaps is shape
%analysis. Shape analysis attempts to reduce the complexity of the
%heap by combining multiple nodes with similar properties into summary
%nodes. The summary nodes typically establish may/must constraints
%over the heap structure, and typically represent an overapproximation
%of the represented heap. As such, program evaluations using shape
%analysis representations are prone to reporting large numbers of
%false positives.
